Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-04 paper/paper.qmd
committing changes to paper.qmd for formatting

### Posterior Predictive Check for the Harris Model
The posterior predictive check for the Harris model illustrates the relationship between the observed support percentages $y$ and the predicted support values $y_{\text{rep}}$. @fig-harris-check displays a density estimate for both the actual observed data (depicted in dark blue) and the predicted values generated by the model (shown in light blue). The purpose of this diagnostic check is to evaluate how well the model captures the distribution of observed support for Kamala Harris.
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-harris-check
#| fig-cap: "Posterior predictive check for Kamala Harris's model, illustrating the distribution of observed support percentages $y$ against the predicted support values $y_{\text{rep}}$. The graph shows a strong correspondence between the observed and predicted distributions, indicating that the model accurately captures the dynamics of voter support for Harris in the given dataset."

@@

print(pp_check_harris)
```
In the plot, we observe a strong overlap between the $y$ and $y_{\text{rep}}$ distributions, with the dark blue curve representing the observed support percentages primarily concentrated around 48% to 52%. This indicates that the model successfully approximates the actual voting support dynamics for Harris. The light blue curves signify the distribution of predicted values, demonstrating the model's ability to replicate the observed trends effectively. The close alignment of the observed and predicted densities suggests that the model adequately reflects the underlying support for Harris among voters, thereby affirming the appropriateness of the model structure. However, similar to the Trump model, the presence of some variability in the predicted values indicates that while the model performs well, there may still be unexplained variations in support levels that could benefit from further analysis. Such limitations are also discussed in @sec-model-diagnostics.

>>>>

### Posterior Predictive Check for the Harris Model
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-harris-check
#| fig-cap: "Posterior predictive check for Kamala Harris's model. Comparison of observed support percentages ($y$) and predicted values ($y_{\text{rep}}$) shows strong alignment, confirming the model's accuracy in capturing voter support dynamics for Harris."

@@

print(pp_check_harris)
```
The posterior predictive check for the Harris model illustrates the relationship between the observed support percentages $y$ and the predicted support values $y_{\text{rep}}$. @fig-harris-check displays a density estimate for both the actual observed data (depicted in dark blue) and the predicted values generated by the model (shown in light blue). The purpose of this diagnostic check is to evaluate how well the model captures the distribution of observed support for Kamala Harris. We observe a strong overlap between the $y$ and $y_{\text{rep}}$ distributions, with the dark blue curve representing the observed support percentages primarily concentrated around 48% to 52%. This indicates that the model successfully approximates the actual voting support dynamics for Harris. The light blue curves signify the distribution of predicted values, demonstrating the model's ability to replicate the observed trends effectively. The close alignment of the observed and predicted densities suggests that the model adequately reflects the underlying support for Harris among voters, thereby affirming the appropriateness of the model structure. However, similar to the Trump model, the presence of some variability in the predicted values indicates that while the model performs well, there may still be unexplained variations in support levels that could benefit from further analysis. Such limitations are also discussed in @sec-model-diagnostics.
